Verification of Stencil Computations through Spatial Specifications

### 2016-07-03 paper.tex
removed duplicate label
added table on tickAssign rates

\begin{figure}
\input{consistency.tex}
\caption{Consistency function for a model and a set of indices}
\label{fig:spatial-model}
\end{figure}

@@

>>>>

\begin{figure}
\input{consistency.tex}
\caption{Consistency function for a model and a set of indices}
\label{fig:consistency}
\end{figure}

@@

\subsection{Occurrences of stencils}

We first examined how frequently stencil computations occur in our
corpus. We define a \emph{potential} statement as one whose left-hand
side is an array subscript on neighbourhood indices. These statements
are the inputs to Step 2 of the Inference process described
Section~\ref{sec:inference}. Each potential statement for which we
eventually generate some stencil specifications for is also counted as
an \emph{actual} statement.

\begin{figure}
\begin{tabular}{|l|l|l|}
\hline
Package       & \% potential & \% actual   \\
\hline
UM            & \umtickAssignPercent &  \umtickAssignSuccessPercent   \\
E3MG          & \ethreemgeatickAssignPercent & \ethreemgeatickAssignSuccessPercent\\
BLAS          & \blastickAssignPercent & \blastickAssignSuccessPercent \\
Hybrid4       & \hybridfourtickAssignPercent & \hybridfourtickAssignPercent \\
GEOS-Chem     & \geoschemtickAssignPercent & \geoschemtickAssignPercent \\
Navier        & \naviertickAssignPercent & \naviertickAssignPercent \\
CP            & \computationalphysicstwotickAssignPercent & \computationalphysicstwotickAssignSuccessPercent\\
\hline
\textbf{Total}& \overalltickAssignPercent  & \overalltickAssignSuccessPercent    \\
\hline 
\end{tabular}
\caption{Stencil assignment rates\label{fig:tickAssign}}
\end{figure}
